---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Supporting Libraries

This analysis makes use of the ggplot2 and dplry libraries for plotting and grouping.
```{r message=FALSE}
library(ggplot2)
library(dplyr)
```
## Loading and preprocessing the data

The data is pulled from the source data file. The data is then cleaned (NA cases removed) and grouped by day and day period.

```{r}
sourceData <- read.csv("./activity.csv")
sourceDataCleaned <- sourceData[complete.cases(sourceData),]
dayGrouped <- group_by(sourceDataCleaned, date)
periodGrouped <- group_by(sourceDataCleaned, interval)
```
## Histogram of the total number of steps taken each day
```{r}
dayTotalSteps <- aggregate( steps ~ date, dayGrouped, sum )
totalStepsPlot <- ggplot(dayTotalSteps, aes(dayTotalSteps$steps)) 
totalStepsPlot + geom_histogram(bins=length(unique(dayGrouped$date))) + xlab("Number of Steps") + ylab("Frequency")
```

## Mean and Median number of steps taken each day
```{r}
mean(sourceData$steps, na.rm = TRUE)
median(sourceData$steps, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r fig.width=12}
periodAverageTotalSteps <- aggregate( steps ~ interval, periodGrouped, mean )
totalStepsPlot <- ggplot(periodAverageTotalSteps, aes(interval, steps)) 
totalStepsPlot + geom_line(stat = "identity") + xlab("Time of Day (minutes)") + ylab("Average Number of Steps")
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
